Effect of resonant and random excitation on the LHC beam in the context of pulsed hollow electron lens operation.

### 2018-02-16 resex.tex
Updated figures of residual fields with 1.24-mm inner diameter.

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}
For a perfectly annular and axially symmetric profile, the field in the region of the proton beam core vanishes as can be seen from Eq.~\ref{eq:field_2} and as illustrated in Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam core thus only arise in case of profile imperfections of the electron beam, in particular if the axial symmetry is broken. Recently, the latest LHC hollow electron gun prototype was characterized at the Fermilab electron lens test stand \cite{hel_test_stand_fnal}. A typical measurement of the electron beam current density is shown in Fig.~\ref{core:fig:0}.
\begin{figure}[t]
		\centering
		\includegraphics[width=0.8\linewidth]{e-field-measured.png}
	\caption{Current density from measurements of the CHG1b hollow electron gun at the Fermilab electron lens test stand in 2017 \cite{hel_res_field_stancari_2017}. \textcolor{red}{Replace by 2D simulations - Giulio.}}
	\label{core:fig:0}
\end{figure}
As at the test stand the solenoidal fields required for the HL-LHC electron lens can not be reached, an estimate of the electron beam profile for HL-LHC can only be obtained through simulations. For this purpose, the measured distribution is compressed to the inner electron beam radius of $0.97$~mm. Afterwards an input distribution with $40\ 000$ particles is generated. As boundary condition, the LHC inner beam pipe radius $b=30$~mm is used. The potential and fields can then be calculated with the particle in cell simulation code WARP~\cite{warp} yielding the relative electric field strengths shown in Fig.~\ref{core:fig:1}. The electric field can in general be scaled with the beam current and energy, but can not easily be scaled with the inner and outer radius of the electron beam distribution. Therefore it is essential to track a distribution with the correct dimensions. Further details on the measurements and WARP simulations can be found in~\cite{hel_res_field_stancari_2017}.
\begin{figure}[h]
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		\includegraphics[width=1.0\linewidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice.png}
	\end{minipage}
	\caption{Calculated relative electric field for the new CHG1b hollow electron gun in the x-y plane (left) and as 1-dimensional cuts though the x- and y-axes (right). The field calculations are based on measurements at the Fermilab test stand combined with WARP  calculations of the electric potentials and fields in a cylindrical beam pipe.}
	\label{core:fig:1}
\end{figure}

>>>>

\subsection{Kicks in the central region (main solenoid)}
\label{core:sec:2}
For a perfectly annular and axially symmetric profile, the field in the region of the proton beam core vanishes as can be seen from Eq.~\ref{eq:field_2} and as illustrated in Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam core thus only arise in case of profile imperfections of the electron beam, in particular if the axial symmetry is broken. Recently, the latest LHC hollow electron gun prototype was characterized at the Fermilab electron lens test stand \cite{hel_test_stand_fnal}. A typical measurement of the electron beam current density is shown in Fig.~\ref{core:fig:0}.
\begin{figure}[t]
		\centering
		\includegraphics[width=0.8\linewidth]{e-field-measured.png}
	\caption{Current density from measurements of the CHG1b hollow electron gun at the Fermilab electron lens test stand in 2017 \cite{hel_res_field_stancari_2017}. \textcolor{red}{Replace by 2D simulations - Giulio.}}
	\label{core:fig:0}
\end{figure}

As at the test stand the solenoidal fields required for the HL-LHC
electron lens can not be reached, an estimate of the electron beam
profile for HL-LHC can only be obtained through simulations. For this
purpose, the measured distribution is compressed to the inner electron
beam radius of 1.24~mm. Afterwards an input distribution with
$40\ 000$ particles is generated. As boundary condition, the LHC inner
beam pipe radius $b=30$~mm is used. The potential and fields can then
be calculated with the particle in cell simulation code
Warp~\cite{warp} yielding the relative electric field strengths shown
in Fig.~\ref{core:fig:1}. The electric field can in general be scaled
with the beam current and energy, but can not easily be scaled with
the inner and outer radius of the electron beam
distribution. Therefore it is essential to track a distribution with
the correct dimensions. Further details on the measurements and Warp
simulations can be found in~\cite{hel_res_field_stancari_2017}.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Emap}
\includegraphics[width=\columnwidth]{CHG1b_170512_8p75A_2-4-2p7kG_500V_76mA_hires_Eslice}
\caption{Calculated relative electric field for the hollow electron
  gun in the transverse $x$-$y$ plane (left) and as 1-dimensional cuts
  through the $x$ and $y$ axes (right). The field calculations are
  based on measurements at the Fermilab electron-lens test stand
  combined with Warp calculations of the electric potentials and
  fields in a cylindrical beam pipe.}
\label{core:fig:1}
\end{figure}
